Reasoning About a Machine with Local Capabilities

### 2019-02-10 toplas/paper.tex
[TOPLAS] Make small textual changes to introduction

  support: an efficient instruction for clearing a range of memory.

@@

  We have made improvements to readability and completeness throughout the paper, but we highlight the following changes:

@@

  \item An introduction to the \sectionname~\nameref{sec:logical-relation} that provides informal intuition about how the logical relation machinery comes into play on a capability machine.

@@

    This section explains how one reasons about common scenarios that arise in programs on a capability machine, and in particular how the logical relation is used.

@@

  \item Details previously found only in the technical appendix~\citep{technical_appendix} to the paper.
    Further, many of the still omitted details have been added to the paper's appendix.

>>>>

  support (wrt CHERI): an efficient instruction for clearing a range of memory.

@@

  We have made improvements to readability and completeness throughout the paper. For instance, we have added an introduction to \sectionname~\nameref{sec:logical-relation} that provides informal intuition about how the logical relation machinery comes into play on a capability machine. We highlight the following changes:

@@

@@

    This section explains how one reasons about common scenarios that arise in programs on a capability machine, and, in particular, how the logical relation is used.

@@

  \item Details previously found only in the technical appendix~\citep{technical_appendix} has been moved to the paper.
    Further, many of the details omitted in the paper has been added to the paper's appendix.
